Are rankings of financial analysts useful to investors?

### 2015-04-01 doc/paper/paper-knitr-APS.tex
Include both sets in the paper

Table (\ref{tab:ret-stat}) shows the distribution of the final sample of target price and EPS data. Panel A shows the number of quarterly target prices per stock. For the sample period (1999-2009), we report 13 672 stock-quarter observations. Each stock had on average of 6.421 quarterly target price reports. Panel B  presents similar statistics of the number of EPS forecasts. In total, the EPS forecast sample has 12 084 stock-quarter observations. The average number of quarterly forecasts is 6.582.

@@

Table (\ref{tab:rank-stat}) shows a contingency analysis of the ranks. 
%Chi square statistics include/ expected frequiency test
%Journ. of Fin economics 
Panel A shows the dynamics of each tercile for rankings based on target price  accuracy. We observe that analysts exhibit strong ranking consistency as, on average, they stay at the same tercile after one quarter. Of the top (bottom) most accurate (inaccurate) analysts in the previous quarter 67.593\% (69.401\%) remain in that same tercile after one quarter. After one year the corresponding figures are lower respectively 46.424\% and 40.681\% for the top and bottom terciles.

@@

Panel A show the statistics for the consensus expectations as defined in eq. (\ref{consq}). The average consensus among the analysts on stock expected returns in the  \tr{}, \naive{} and \default{} information sets are, respectively, NA\%, 18.993\%, and 18.993\% respectively. Panel B of the table shows the TP accuracy weighted average expected returns (15.191\%, 16.098\%, and 12.718\%). Panel C shows the EPS based weighted expected returns averages (14.774\%, 14.967\%, and 12.928\%).

@@

\subsection{Perfect foresight strategy}
\label{sec:perfect}
Panel B presents the results for the case of the \tr{} information set. The annualized cumulative returns for each of the active strategies (\textit{CONS}, \textit{TP}, and \textit{EPS}) are, respectively, NA\%, 4.512\%, 0.718\%. All the strategies outperform the passive benchmark (\ensuremath{-3.032}\%). The results show, as expected, that  we would better off if we knew in advance who the top analysts in terms of TP accuracy would be. In any case, the results suggest that the advice of analysts, as a group, is valuable. 
%Yet, the top analyst

@@

The \textit{TP} ranking strategy dominates also when we look at the risk-adjusted returns. The Sharpe Ratio is 0.305 against NA, 0.046, and \ensuremath{-0.182}, respectively for the \textit{CONS}, the \textit{EPS}, and the \textit{Market} strategies. In addition, the \textit{TP} strategy dominates  the others if we consider the smaller trading periods (5 years). Table \ref{tab:substrategy} shows the Sharpe Ratio for six 5-year holding periods. The \textit{TP} strategy wins over the others in every period as expected.

@@

\subsection{Feasible strategies}
Panel C of table (\ref{tab:strategy}) shows the performance of the different smart strategies in the \naive{} information set. As it was the  case of the \tr{} information set, all the active strategies outperform the \textit{Market} (\ensuremath{-3.032}\%)  and show positive cumulative annualized returns of 0.622\%,  0.449\%, \ensuremath{-0.361}\% respectively for the \textit{TP}, the \textit{CONS}, and the \textit{EPS} strategies. Similarly, the \textit{TP} strategy dominates when we consider the risk-adjusted returns. The Sharpe Ratio for this strategy is 0.04 which is higher than that Sharpe Ratios of the \textit{CONS} and  the \textit{EPS} strategies  (0.028 and \ensuremath{-0.022} respectively). The results in panel B of table \ref{tab:substrategy} show as well that this strategy outperform the others for all of 5 trading sub-periods.

Panel D of table \ref{tab:strategy} confirm the outperformance of the \textit{TP} smart strategy: this is the the only active strategy that yields positive annualized cumulative return (1.043\%) whereas both  the \textit{CONS} and the \textit{EPS} show negative returns (0.702\% and 0.711\% respectively). The panel C of table \ref{tab:substrategy} shows that the Sharpe Ratio of the \textit{TP} strategy is lower then that of the \textit{EPS} strategy in only first two sub-periods (2000Q1/2004Q4 and 2001Q1/2005Q4).

@@

\begin{tabularx}{\linewidth}{r*{6}{Y}}
    \toprule
Year & Min& Mean & Median &Max& Std.dev\\
\midrule
%Panel A: TP&&&&&\\
\multicolumn{6}{c}{\textbf{Panel A: TP}} \\
\midrule
%Year & Min& Mean & Median &Max& Std.dev\\
 1999 &    3 & 4.246 & 4 &   10 & 1.588 \\ 
  2000 &    3 & 4.756 & 4 &   14 & 1.878 \\ 
  2001 &    3 & 5.248 & 5 &   15 & 2.323 \\ 
  2002 &    3 & 6.043 & 5 &   19 & 2.948 \\ 
  2003 &    3 & 6.667 & 6 &   21 & 3.427 \\ 
  2004 &    3 & 7.120 & 6 &   21 & 3.617 \\ 
  2005 &    3 & 7.348 & 7 &   21 & 3.592 \\ 
  2006 &    3 & 7.408 & 7 &   20 & 3.417 \\ 
  2007 &    3 & 7.050 & 6 &   20 & 3.334 \\ 
  2008 &    3 & 6.370 & 6 &   18 & 2.884 \\ 
  2009 &    3 & 5.152 & 5 &   18 & 2.191 \\ 
   \midrule 
Total &    3 & 6.421 & 6 &   21 & 3.210 \\

@@

 &$top$ & 67.7 & 22.1 & 10.2 & 100.0 \\ 
  &$middle$ & 29.9 & 48.2 & 21.9 & 100.0 \\ 
  &$bottom$ & 13.4 & 17.1 & 69.6 & 100.0 \\ 
    &&\multicolumn{4}{c}{$t+4$}\\ 
&$top$ & 46.2 & 28.0 & 25.8 & 100.0 \\ 
  &$middle$ & 39.2 & 29.2 & 31.6 & 100.0 \\ 
  &$bottom$ & 32.1 & 26.7 & 41.2 & 100.0 \\

\end{tabularx}
\begin{tabularx}{\linewidth}{r*{6}{Y}}
\midrule
\multirow{11}{*}{$t$}&\textbf{Panel B: EPS}&\multicolumn{4}{c}{$t+1$} \\
&&$top$&$middle$&$bottom$&Sum\\
 &$top$ & 48.4 & 26.1 & 26.0 & 100.5 \\ 
  &$middle$ & 48.2 & 26.2 & 25.8 & 100.4 \\ 
  &$bottom$ & 46.3 & 25.9 & 28.5 & 100.8 \\ 
    &&\multicolumn{4}{c}{$t+4$}\\ 
&$top$ & 46.8 & 28.3 & 26.0 & 101.1 \\ 
  &$middle$ & 45.5 & 27.0 & 28.1 & 100.6 \\ 
  &$bottom$ & 42.7 & 27.6 & 32.4 & 102.7 \\

@@

\begin{tabularx}{\linewidth}{r*{4}{Y}}
\toprule
& Mean (in \%)&Median (in \%)&Std.dev\\
%&all&same&all&same&all&same\\
\midrule
  \multicolumn{4}{c}{\textbf{Panel A: Consensus}} \\ 
 \midrule 
\tr{} & - & - & - \\ 
  \naive{} & 18.993 & 17.173 & 0.119 \\ 
  \default{} & 18.993 & 17.173 & 0.119 \\

@@

\begin{tabularx}{\linewidth}{r*{4}{Y}}
  \midrule
  \multicolumn{4}{c}{\textbf{Panel B: TP}} \\ 
 \midrule 
\tr{} & 15.191 & 13.595 & 0.096 \\ 
  \naive{} & 16.098 & 14.528 & 0.098 \\ 
  \default{} & 12.718 & 10.789 & 0.089 \\

@@

\begin{tabularx}{\linewidth}{r*{4}{Y}}
  \multicolumn{4}{c}{\textbf{Panel C: EPS}} \\ 
 \midrule 
\tr{} & 14.774 & 13.269 & 0.102 \\ 
  \naive{} & 14.967 & 13.432 & 0.103 \\ 
  \default{} & 12.928 & 11.440 & 0.089 \\

@@

%\resizebox{\textwidth}{!}{%
%\begin{tabular}{rrrrrrr}
\begin{tabularx}{\linewidth}{r*{4}{Y}}
\toprule
Year&\textit{CONS}& \textit{TP} &\textit{EPS}\\
%&all&same&all&same&all&same\\
  \multicolumn{4}{l}{\textbf{Panel A: \tr{}}} \\ 
 \midrule 
1999 & - &   69 &   44 \\ 
  2000 & - &  232 &  191 \\ 
  2001 & - &  273 &  244 \\ 
  2002 & - &  317 &  290 \\ 
  2003 & - &  330 &  299 \\ 
  2004 & - &  331 &  318 \\ 
  2005 & - &  347 &  337 \\ 
  2006 & - &  351 &  337 \\ 
  2007 & - &  359 &  351 \\ 
  2008 & - &  354 &  339 \\ 
  2009 & - &  306 &  306 \\ 
   \midrule 
Total & - &  378 &  375 \\

@@

\begin{tabularx}{\linewidth}{r*{4}{Y}}
  \multicolumn{4}{l}{\textbf{Panel B: \naive{}}} \\ 
 \midrule 
1999 &   69 &   69 &   44 \\ 
  2000 &  235 &  235 &  186 \\ 
  2001 &  281 &  281 &  247 \\ 
  2002 &  323 &  323 &  288 \\ 
  2003 &  334 &  334 &  307 \\ 
  2004 &  341 &  341 &  318 \\ 
  2005 &  352 &  352 &  337 \\ 
  2006 &  358 &  358 &  343 \\ 
  2007 &  361 &  361 &  352 \\ 
  2008 &  360 &  360 &  349 \\ 
  2009 &  351 &  351 &  321 \\ 
   \midrule 
Total &  378 &  378 &  376 \\

@@

\begin{tabularx}{\linewidth}{r*{4}{Y}}
  \multicolumn{4}{l}{\textbf{Panel C: \default{}}} \\ 
 \midrule 
1999 &   69 &   69 &   54 \\ 
  2000 &  235 &  235 &  204 \\ 
  2001 &  281 &  281 &  261 \\ 
  2002 &  323 &  323 &  304 \\ 
  2003 &  334 &  334 &  317 \\ 
  2004 &  341 &  341 &  332 \\ 
  2005 &  352 &  352 &  344 \\ 
  2006 &  358 &  358 &  353 \\ 
  2007 &  361 &  361 &  358 \\ 
  2008 &  360 &  360 &  359 \\ 
  2009 &  351 &  351 &  350 \\ 
   \midrule 
Total &  378 &  378 &  377 \\

@@

\begin{tabularx}{\linewidth}{r*{6}{Y}}
  \toprule
  %\multicolumn{5}{l}{\textbf{Panel A: Market}} \\
Strategy&Annualized return (in \%)&Annualized Std. dev (in \%)&Sharpe ratio&Average num. stock&Average turnover rate \\  \multicolumn{6}{l}{\textbf{Panel A}} \\ 
\textit{Market} & -3.032 & 16.654 & -0.182 &  499 & 0.053 \\ 
  \midrule

@@

\begin{tabularx}{\linewidth}{r*{6}{Y}}
\multicolumn{6}{l}{\textbf{Panel B: \tr{} }} \\

 \textit{CONS} & - & - & - & - & - \\ 
  \textit{TP} & 4.512 & 14.792 & 0.305 &  251 & 0.326 \\ 
  \textit{EPS} & 0.718 & 15.509 & 0.046 &  205 & 0.493 \\ 
   \midrule

\begin{tabularx}{\linewidth}{r*{6}{Y}}
  \multicolumn{6}{l}{\textbf{Panel C: \naive{}}} \\
 \textit{CONS} & 0.449 & 15.993 & 0.028 &  252 & 0.250 \\ 
  \textit{TP} & 0.622 & 15.682 & 0.040 &  252 & 0.256 \\ 
  \textit{EPS} & -0.361 & 16.100 & -0.022 &  206 & 0.408 \\ 
   \midrule

\begin{tabularx}{\linewidth}{r*{6}{Y}}
  \multicolumn{6}{l}{\textbf{Panel D: \default{}}} \\
 \textit{CONS} & 0.702 & 15.820 & 0.044 &  252 & 0.223 \\ 
  \textit{TP} & 1.043 & 15.476 & 0.067 &  252 & 0.248 \\ 
  \textit{EPS} & 0.711 & 15.481 & 0.046 &  245 & 0.255 \\

@@

  \multicolumn{9}{l}{\textbf{Panel A: \tr{}}} \\
2000Q1/2004Q4 & -3.401 & -0.201 & - & - & 6.545 & 0.447 & 2.080 & 0.137 \\ 
  2001Q1/2005Q4 & -1.539 & -0.093 & - & - & 6.185 & 0.429 & 4.076 & 0.279 \\ 
  2002Q1/2006Q4 & 2.567 & 0.196 & - & - & 8.985 & 0.768 & 5.822 & 0.485 \\ 
  2003Q1/2007Q4 & 7.919 & 0.925 & - & - & 14.236 & 1.889 & 10.690 & 1.365 \\ 
  2004Q1/2008Q4 & -5.667 & -0.435 & - & - & 0.399 & 0.030 & -3.083 & -0.229 \\ 
  2005Q1/2009Q4 & -2.662 & -0.158 & - & - & 2.518 & 0.165 & -0.625 & -0.039 \\ 
   \midrule 
All period & -3.032 & -0.182 & - & - & 4.512 & 0.305 & 0.718 & 0.046 \\

@@

\resizebox{\textwidth}{!}{%
\begin{tabular}{rrrrrrrrr}
%\begin{tabularx}{\linewidth}{r*{9}{Y}}
  \multicolumn{9}{l}{\textbf{Panel B: \naive{}}} \\
2000Q1/2004Q4 & -3.401 & -0.201 & 3.401 & 0.215 & 3.345 & 0.217 & 1.045 & 0.066 \\ 
  2001Q1/2005Q4 & -1.539 & -0.093 & 2.840 & 0.180 & 3.538 & 0.232 & 2.537 & 0.163 \\ 
  2002Q1/2006Q4 & 2.567 & 0.196 & 5.837 & 0.468 & 6.229 & 0.517 & 5.415 & 0.448 \\ 
  2003Q1/2007Q4 & 7.919 & 0.925 & 9.410 & 1.098 & 9.965 & 1.242 & 9.298 & 1.149 \\ 
  2004Q1/2008Q4 & -5.667 & -0.435 & -4.826 & -0.349 & -4.254 & -0.311 & -4.551 & -0.333 \\ 
  2005Q1/2009Q4 & -2.662 & -0.158 & -2.419 & -0.147 & -2.029 & -0.125 & -1.748 & -0.105 \\ 
   \midrule 
All period & -3.032 & -0.182 & 0.449 & 0.028 & 0.622 & 0.040 & -0.361 & -0.022 \\

\midrule
\end{tabular}}
\resizebox{\textwidth}{!}{%
\begin{tabular}{rrrrrrrrr}
%\begin{tabularx}{\linewidth}{r*{9}{Y}}
  \multicolumn{5}{l}{\textbf{Panel C: \default{}}} \\
2000Q1/2004Q4 & -3.401 & -0.201 & 3.934 & 0.252 & 3.833 & 0.256 & 3.470 & 0.229 \\ 
  2001Q1/2005Q4 & -1.539 & -0.093 & 3.278 & 0.211 & 4.000 & 0.270 & 3.883 & 0.259 \\ 
  2002Q1/2006Q4 & 2.567 & 0.196 & 5.464 & 0.433 & 5.907 & 0.487 & 5.686 & 0.465 \\ 
  2003Q1/2007Q4 & 7.919 & 0.925 & 9.285 & 1.066 & 10.185 & 1.252 & 9.964 & 1.195 \\ 
  2004Q1/2008Q4 & -5.667 & -0.435 & -4.979 & -0.364 & -4.093 & -0.299 & -4.251 & -0.311 \\ 
  2005Q1/2009Q4 & -2.662 & -0.158 & -2.429 & -0.149 & -1.671 & -0.103 & -1.974 & -0.122 \\ 
   \midrule 
All period & -3.032 & -0.182 & 0.702 & 0.044 & 1.043 & 0.067 & 0.711 & 0.046 \\

>>>>

Table (\ref{tab:ret-stat}) shows the distribution of the final sample of target price and EPS data. Panel A shows the number of quarterly target prices per stock. For the sample period (1999-2009), we report 15 048 stock-quarter observations. Each stock had on average of 12.823 quarterly target price reports. Panel B  presents similar statistics of the number of EPS forecasts. In total, the EPS forecast sample has 12 084 stock-quarter observations. The average number of quarterly forecasts is 6.582.

@@

Table (\ref{tab:rank-stat}) shows a contingency analysis of the ranks. 
%Chi square statistics include/ expected frequiency test
%Journ. of Fin economics 
Panel A shows the dynamics of each tercile for rankings based on target price  accuracy. We observe that analysts exhibit strong ranking consistency as, on average, they stay at the same tercile after one quarter. Of the top (bottom) most accurate (inaccurate) analysts in the previous quarter 67.58\% (69.37\%) remain in that same tercile after one quarter. After one year the corresponding figures are lower respectively 46.568\% and 40.877\% for the top and bottom terciles.

@@

Panel A show the statistics for the consensus expectations as defined in eq. (\ref{consq}). The average consensus among the analysts on stock expected returns in the  \tr{}, \naive{} and \default{} information sets are, respectively, NA\%, 18.61\%, and 18.61\% respectively. Panel B of the table shows the TP accuracy weighted average expected returns (14.876\%, 15.742\%, and 12.459\%). Panel C shows the EPS based weighted expected returns averages (14.689\%, 14.884\%, and 12.843\%).

@@

\subsection{Perfect foresight strategy}
\label{sec:perfect}
Panel B presents the results for the case of the \tr{} information set. The annualized cumulative returns for each of the active strategies (\textit{CONS}, \textit{TP}, and \textit{EPS}) are, respectively, NA\%, 4.325\%, 0.574\%. All the strategies outperform the passive benchmark (\ensuremath{-3.032}\%). The results show, as expected, that  we would better off if we knew in advance who the top analysts in terms of TP accuracy would be. In any case, the results suggest that the advice of analysts, as a group, is valuable. 
%Yet, the top analyst

@@

The \textit{TP} ranking strategy dominates also when we look at the risk-adjusted returns. The Sharpe Ratio is 0.294 against NA, 0.037, and \ensuremath{-0.182}, respectively for the \textit{CONS}, the \textit{EPS}, and the \textit{Market} strategies. In addition, the \textit{TP} strategy dominates  the others if we consider the smaller trading periods (5 years). Table \ref{tab:substrategy} shows the Sharpe Ratio for six 5-year holding periods. The \textit{TP} strategy wins over the others in every period as expected.

@@

\subsection{Feasible strategies}
Panel C of table (\ref{tab:strategy}) shows the performance of the different smart strategies in the \naive{} information set. As it was the  case of the \tr{} information set, all the active strategies outperform the \textit{Market} (\ensuremath{-3.032}\%)  and show positive cumulative annualized returns of 0.282\%,  0.116\%, \ensuremath{-0.303}\% respectively for the \textit{TP}, the \textit{CONS}, and the \textit{EPS} strategies. Similarly, the \textit{TP} strategy dominates when we consider the risk-adjusted returns. The Sharpe Ratio for this strategy is 0.018 which is higher than that Sharpe Ratios of the \textit{CONS} and  the \textit{EPS} strategies  (0.007 and \ensuremath{-0.019} respectively). The results in panel B of table \ref{tab:substrategy} show as well that this strategy outperform the others for all of 5 trading sub-periods.

Panel D of table \ref{tab:strategy} confirm the outperformance of the \textit{TP} smart strategy: this is the the only active strategy that yields positive annualized cumulative return (0.689\%) whereas both  the \textit{CONS} and the \textit{EPS} show negative returns (0.314\% and 0.746\% respectively). The panel C of table \ref{tab:substrategy} shows that the Sharpe Ratio of the \textit{TP} strategy is lower then that of the \textit{EPS} strategy in only first two sub-periods (2000Q1/2004Q4 and 2001Q1/2005Q4).

@@

\begin{tabularx}{\linewidth}{r*{6}{Y}}
    \toprule
Year & Min& Mean & Median &Max& Std.dev\\
\midrule
%Panel A: TP&&&&&\\
\multicolumn{6}{c}{\textbf{Panel A: TP}} \\
\midrule
%Year & Min& Mean & Median &Max& Std.dev\\
\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in `display<-.xtable`(`*tmp*`, value = c("{}s"{}, "{}f"{}, "{}d"{}, "{}f"{}, "{}f"{}, : "{}display"{} must have length equal to 8 ( ncol(x) + 1 )}}\end{kframe}
\end{tabularx}

@@

 &$top$ & 67.6 & 22.2 & 10.3 & 100.0 \\ 
  &$middle$ & 30.5 & 47.8 & 21.7 & 100.0 \\ 
  &$bottom$ & 13.7 & 16.9 & 69.4 & 100.0 \\ 
    &&\multicolumn{4}{c}{$t+4$}\\ 
&$top$ & 46.6 & 27.9 & 25.6 & 100.0 \\ 
  &$middle$ & 39.0 & 29.1 & 31.9 & 100.0 \\ 
  &$bottom$ & 32.7 & 26.4 & 40.9 & 100.0 \\

\end{tabularx}
\begin{tabularx}{\linewidth}{r*{6}{Y}}
\midrule
\multirow{11}{*}{$t$}&\textbf{Panel B: EPS}&\multicolumn{4}{c}{$t+1$} \\
&&$top$&$middle$&$bottom$&Sum\\
 &$top$ & 48.4 & 26.1 & 26.0 & 100.5 \\ 
  &$middle$ & 48.1 & 26.3 & 25.9 & 100.4 \\ 
  &$bottom$ & 46.5 & 25.7 & 28.6 & 100.8 \\ 
    &&\multicolumn{4}{c}{$t+4$}\\ 
&$top$ & 46.7 & 28.4 & 26.1 & 101.1 \\ 
  &$middle$ & 45.4 & 27.1 & 28.1 & 100.6 \\ 
  &$bottom$ & 42.8 & 27.7 & 32.3 & 102.7 \\

@@

\begin{tabularx}{\linewidth}{r*{7}{Y}}
\toprule
& \multicolumn{2}{c}{Mean (in \%)}&\multicolumn{2}{c}{Median (in \%)}& \multicolumn{2}{c}{Std.dev}\\
&all&same&all&same&all&same\\
\midrule
  \multicolumn{7}{c}{\textbf{Panel A: Consensus}} \\ 
 \midrule 
\tr{} & - & - & - & - & - & - \\ 
  \naive{} & 18.610 & 18.985 & 16.889 & 17.185 & 0.120 & 0.119 \\ 
  \default{} & 18.610 & 18.985 & 16.889 & 17.185 & 0.120 & 0.119 \\

@@

\begin{tabularx}{\linewidth}{r*{7}{Y}}
  \midrule
  \multicolumn{7}{c}{\textbf{Panel B: TP}} \\ 
 \midrule 
\tr{} & 14.876 & 15.191 & 13.380 & 13.604 & 0.096 & 0.096 \\ 
  \naive{} & 15.742 & 16.102 & 14.314 & 14.541 & 0.098 & 0.098 \\ 
  \default{} & 12.459 & 12.714 & 10.591 & 10.798 & 0.089 & 0.089 \\

@@

\begin{tabularx}{\linewidth}{r*{7}{Y}}
  \multicolumn{7}{c}{\textbf{Panel C: EPS}} \\ 
 \midrule 
\tr{} & 14.689 & 14.769 & 13.214 & 13.252 & 0.101 & 0.102 \\ 
  \naive{} & 14.884 & 14.959 & 13.392 & 13.420 & 0.103 & 0.103 \\ 
  \default{} & 12.843 & 12.916 & 11.410 & 11.439 & 0.089 & 0.089 \\

@@

%\resizebox{\textwidth}{!}{%
%\begin{tabular}{rrrrrrr}
\begin{tabularx}{\linewidth}{r*{7}{Y}}
\toprule
Year&\multicolumn{2}{c}{\textit{CONS}}& \multicolumn{2}{c}{\textit{TP}} &\multicolumn{2}{c}{\textit{EPS}}\\
&all&same&all&same&all&same\\
  \multicolumn{7}{l}{\textbf{Panel A: \tr{}}} \\ 
 \midrule 
1999 & - & - &   71 &   67 &   42 &   42 \\ 
  2000 & - & - &  253 &  232 &  191 &  191 \\ 
  2001 & - & - &  302 &  273 &  244 &  244 \\ 
  2002 & - & - &  353 &  316 &  289 &  289 \\ 
  2003 & - & - &  369 &  330 &  299 &  299 \\ 
  2004 & - & - &  375 &  331 &  318 &  318 \\ 
  2005 & - & - &  395 &  347 &  337 &  337 \\ 
  2006 & - & - &  403 &  351 &  337 &  337 \\ 
  2007 & - & - &  418 &  359 &  351 &  351 \\ 
  2008 & - & - &  413 &  353 &  339 &  339 \\ 
  2009 & - & - &  346 &  306 &  306 &  306 \\ 
   \midrule 
Total & - & - &  442 &  378 &  375 &  375 \\

@@

\begin{tabularx}{\linewidth}{r*{7}{Y}}
  \multicolumn{7}{l}{\textbf{Panel B: \naive{}}} \\ 
 \midrule 
1999 &   71 &   67 &   71 &   67 &   41 &   41 \\ 
  2000 &  257 &  235 &  257 &  235 &  185 &  186 \\ 
  2001 &  310 &  281 &  310 &  281 &  247 &  247 \\ 
  2002 &  360 &  321 &  360 &  321 &  287 &  287 \\ 
  2003 &  374 &  334 &  374 &  334 &  307 &  307 \\ 
  2004 &  385 &  341 &  385 &  341 &  318 &  318 \\ 
  2005 &  401 &  352 &  401 &  352 &  337 &  337 \\ 
  2006 &  415 &  358 &  415 &  358 &  343 &  343 \\ 
  2007 &  421 &  361 &  421 &  361 &  352 &  352 \\ 
  2008 &  422 &  360 &  422 &  360 &  349 &  349 \\ 
  2009 &  405 &  351 &  405 &  351 &  321 &  321 \\ 
   \midrule 
Total &  442 &  378 &  442 &  378 &  376 &  376 \\

@@

\begin{tabularx}{\linewidth}{r*{7}{Y}}
  \multicolumn{7}{l}{\textbf{Panel C: \default{}}} \\ 
 \midrule 
1999 &   71 &   67 &   71 &   67 &   51 &   51 \\ 
  2000 &  257 &  235 &  257 &  235 &  204 &  204 \\ 
  2001 &  310 &  281 &  310 &  281 &  261 &  261 \\ 
  2002 &  360 &  321 &  360 &  321 &  302 &  302 \\ 
  2003 &  374 &  334 &  374 &  334 &  317 &  317 \\ 
  2004 &  385 &  341 &  385 &  341 &  332 &  332 \\ 
  2005 &  401 &  352 &  401 &  352 &  344 &  344 \\ 
  2006 &  415 &  358 &  415 &  358 &  353 &  353 \\ 
  2007 &  421 &  361 &  421 &  361 &  358 &  358 \\ 
  2008 &  422 &  360 &  422 &  360 &  359 &  359 \\ 
  2009 &  405 &  351 &  405 &  351 &  350 &  350 \\ 
   \midrule 
Total &  442 &  378 &  442 &  378 &  377 &  377 \\

@@

\begin{tabularx}{\linewidth}{r*{5}{Y}}
  \toprule
  %\multicolumn{5}{l}{\textbf{Panel A: Market}} \\
Strategy&Annualized return (in \%)&Annualized Std. dev (in \%)&Sharpe ratio&Average num. stock&Average turnover rate \\  \multicolumn{5}{l}{\textbf{Panel A}} \\ 
\textit{Market} & -3.032 & 16.654 & -0.182 &  499 & 0.053 \\ 
  \midrule

@@

\resizebox{\textwidth}{!}{%
\begin{tabular}{rrrrrrrrrrr}
  \multicolumn{11}{c}{\textbf{Panel B: \tr{} }} \\
  &all&same&all&same&all&same&all&same&all&same \\

 \textit{CONS} & - & - & - & - & - & - & - & - & - & - \\ 
  \textit{TP} & 4.325 & 4.549 & 14.697 & 14.794 & 0.294 & 0.307 &  283 &  251 & 0.345 & 0.327 \\ 
  \textit{EPS} & 0.574 & 0.719 & 15.528 & 15.505 & 0.037 & 0.046 &  205 &  205 & 0.496 & 0.494 \\ 
   \midrule

\end{tabular}}

\resizebox{\textwidth}{!}{%
\begin{tabular}{rrrrrrrrrrr}
  \multicolumn{11}{c}{\textbf{Panel C: \naive{}}} \\
 \textit{CONS} & 0.116 & 0.434 & 15.948 & 15.995 & 0.007 & 0.027 &  283 &  251 & 0.256 & 0.251 \\ 
  \textit{TP} & 0.282 & 0.621 & 15.662 & 15.682 & 0.018 & 0.040 &  284 &  251 & 0.264 & 0.256 \\ 
  \textit{EPS} & -0.303 & -0.349 & 16.088 & 16.096 & -0.019 & -0.022 &  206 &  206 & 0.410 & 0.408 \\ 
   \midrule

\end{tabular}}

\resizebox{\textwidth}{!}{%
\begin{tabular}{rrrrrrrrrrr}
  \multicolumn{11}{c}{\textbf{Panel D: \default{}}} \\
 \textit{CONS} & 0.314 & 0.686 & 15.773 & 15.825 & 0.020 & 0.043 &  283 &  251 & 0.228 & 0.223 \\ 
  \textit{TP} & 0.689 & 1.056 & 15.565 & 15.485 & 0.044 & 0.068 &  284 &  251 & 0.256 & 0.248 \\ 
  \textit{EPS} & 0.746 & 0.717 & 15.444 & 15.481 & 0.048 & 0.046 &  245 &  245 & 0.256 & 0.256 \\

@@

  \multicolumn{9}{l}{\textbf{Panel A: \tr{}}} \\
2000Q1/2004Q4 & -3.401 & -0.201 & - & - & 5.844 & 0.395 & 1.890 & 0.124 \\ 
  2001Q1/2005Q4 & -1.539 & -0.093 & - & - & 6.119 & 0.425 & 3.945 & 0.270 \\ 
  2002Q1/2006Q4 & 2.567 & 0.196 & - & - & 9.124 & 0.757 & 5.877 & 0.492 \\ 
  2003Q1/2007Q4 & 7.919 & 0.925 & - & - & 14.715 & 1.915 & 10.681 & 1.364 \\ 
  2004Q1/2008Q4 & -5.667 & -0.435 & - & - & 0.908 & 0.070 & -3.133 & -0.232 \\ 
  2005Q1/2009Q4 & -2.662 & -0.158 & - & - & 2.827 & 0.189 & -0.725 & -0.045 \\ 
   \midrule 
All period & -3.032 & -0.182 & - & - & 4.325 & 0.294 & 0.574 & 0.037 \\

@@

\resizebox{\textwidth}{!}{%
\begin{tabular}{rrrrrrrrr}
%\begin{tabularx}{\linewidth}{r*{9}{Y}}
  \multicolumn{9}{l}{\textbf{Panel B: \naive{}}} \\
2000Q1/2004Q4 & -3.401 & -0.201 & 2.663 & 0.167 & 2.620 & 0.168 & 1.172 & 0.074 \\ 
  2001Q1/2005Q4 & -1.539 & -0.093 & 2.669 & 0.170 & 3.266 & 0.214 & 2.659 & 0.171 \\ 
  2002Q1/2006Q4 & 2.567 & 0.196 & 5.734 & 0.447 & 6.075 & 0.490 & 5.485 & 0.455 \\ 
  2003Q1/2007Q4 & 7.919 & 0.925 & 9.548 & 1.106 & 10.068 & 1.248 & 9.337 & 1.155 \\ 
  2004Q1/2008Q4 & -5.667 & -0.435 & -4.708 & -0.343 & -4.148 & -0.305 & -4.541 & -0.332 \\ 
  2005Q1/2009Q4 & -2.662 & -0.158 & -2.367 & -0.146 & -2.003 & -0.125 & -1.757 & -0.106 \\ 
   \midrule 
All period & -3.032 & -0.182 & 0.116 & 0.007 & 0.282 & 0.018 & -0.303 & -0.019 \\

\midrule
\end{tabular}}
\resizebox{\textwidth}{!}{%
\begin{tabular}{rrrrrrrrr}
%\begin{tabularx}{\linewidth}{r*{9}{Y}}
  \multicolumn{5}{l}{\textbf{Panel C: \default{}}} \\
2000Q1/2004Q4 & -3.401 & -0.201 & 3.102 & 0.197 & 3.133 & 0.205 & 3.501 & 0.232 \\ 
  2001Q1/2005Q4 & -1.539 & -0.093 & 3.016 & 0.194 & 3.727 & 0.249 & 3.954 & 0.264 \\ 
  2002Q1/2006Q4 & 2.567 & 0.196 & 5.410 & 0.417 & 5.793 & 0.464 & 5.712 & 0.468 \\ 
  2003Q1/2007Q4 & 7.919 & 0.925 & 9.419 & 1.071 & 10.335 & 1.245 & 10.002 & 1.202 \\ 
  2004Q1/2008Q4 & -5.667 & -0.435 & -4.860 & -0.358 & -3.941 & -0.289 & -4.223 & -0.309 \\ 
  2005Q1/2009Q4 & -2.662 & -0.158 & -2.398 & -0.149 & -1.697 & -0.105 & -1.936 & -0.121 \\ 
   \midrule 
All period & -3.032 & -0.182 & 0.314 & 0.020 & 0.689 & 0.044 & 0.746 & 0.048 \\
